A survey of HTTP caching options on the open Web

### 2015-01-12 sanity/paper1.tex
start of conditionals
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@960 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

\subsection{Cache validation}

Hitherto, we have considered the case where the client or proxy does
not send a HTTP request to the server when a resource that is present
in the cache is requested. This is desireable if the client can be
sufficiently confident that the response is fresh, either by having a
standards-compliant freshness lifetime or a heuristic to determine
it. At the end of this period, or if the previous response had no
lifetime, due to lack of information, or to that the server has stated
so in the \httph{Cache-Control} header, responses must be
revalidated. In this case, RFC7232 defines the behaviour, with
\httph{ETag} and \httph{Last-Modified} as the relevant response
headers.
